Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-04 paper/paper.tex
definition of pp, related work before design outline

@@

>>>>

Anglican is a language for expressing probabilistic programs.
A probabilistic program is a stateful \textit{deterministic} computation
$\mathcal{P}$ with the following properties~\cite{TMP+15}:
\begin{itemize}
\item Initially, $\mathcal{P}$ expects no arguments.
\item On every call, $\mathcal{P}$ returns either a distribution
  and an address $(F,\alpha)$, a distribution and a value $(G, y)$, a
  value $z$, or $\bot$.
\item Upon returning $F$, $\mathcal{P}$ expects a value $x$ drawn from $F$ as
  the argument to the next call.
\item Upon returning $(G, y)$ or $z$, $\mathcal{P}$ is invoked again
  without arguments.
\item Upon returning $\bot$, $\mathcal{P}$ terminates.
\end{itemize}
A program is run by calling $\mathcal{P}$ repeatedly until
termination.

A program need not generate the same sequence of random variables in
every execution. For this reason we assume that each random variable
$x$ is assigned a unique label $\alpha$, which we call an address,
that induces a correspondence between variables in different
executions. Every execution implicitly produces a sequence of triples
of distributions, values of \textit{latent} random variables, and
addresses, $(F_i, x_i, \alpha_i)$.  We call this sequence a
\textit{trace} and denote it by $\pmb{x}$. A trace induces a sequence
of pairs $(G_j, y_j)$ of distributions and values of
\textit{observed} random variables. We call this
sequence an \textit{image} and denote it by $\pmb{y}$. For notational simplicity we assume that the program always generates the same ordered set $\pmb{z}$ of \textit{output} values $z_k$.

The target density $\pi(\vec{x}) := \gamma(\vec{x}) / Z$ of a program
is defined in terms of the product of the probabilities of all random
choices $\pmb{x}$ and the likelihood of all observations $\pmb{y}$
\begin{align}
  \gamma(\pmb{x}) 
  &:= 
  \prod_{i=1}^{\left|\pmb{x}\right|}
  p_{F_i}(x_i) \prod_{j=1}^{\left|\pmb{y}\right|}p_{G_j}(y_{j}).
  \label{eqn:p-trace}
\end{align}
The objective of inference in probabilistic program $\mathcal{P}$
is to discover the distribution of $\pmb{z}$.

@@

\subsection{Syntax}
